### 2024-08-24 chapters/stbf_struct.tex
Add figures

	\begin{figure}[p]
		\includegraphics[width=\linewidth]{part2/figures/stbf_struct/covs.eps}
		\caption{Different estimators of the covariance and inverse covariance
			of 100 epochs of data from \textit{Subject 01} for channels
			\textit{Fz}, \textit{Cz}, \textit{Pz}, and \textit{Oz} and time samples between 0.1s and 0.6s.
			Regularized estimators of the inverse covariance exhibit less extreme values and have a sparser structure.
			(\textbf{a,b}) Empirical covariance and inverse covariance matrices.
			(\textbf{c,d}) Shrunk covariance and inverse covariance matrices with $\alpha=0.14$ as
			determined by the closed-form LOOCV method. (\textbf{e,f}) Kronecker-Toeplitz
			structured covariance and inverse covariance matrices.
			(\textbf{g,h}) Spatial Kronecker factor of the Kronecker-Toeplitz structured shrunk estimator and its inverse.
			(\textbf{i,j}) Temporal Kronecker factor of the Kronecker-Toeplitz structured shrunk estimator and its inverse.}
		\label{fig:kronlda-covs}
	\end{figure}
	\todo{visualize kronecker sum}
	\todo{visualize kronpca decomp pvl}
	\todo{method pvl}

@@

	\begin{figure}
		%\includegraphics[width=\linewidth]{figures/fpi.eps}
		\caption{Average cross-validated \textsc{stbf-struct} Accuracy using
			one trial per block over all 21 subjects
			relative to the number of iterations used to estimate the Kronecker-Toeplitz structured shrunk
			covariance. Error bars represent the first and third quartiles. The
			accuracy does not improve when using more than one iteration.
			(\textbf{a}) Results for 1, 2, and 5 trials using only the first block in each
			training fold for training. (\textbf{b}) Results
			for 1, 2, and 5 trials using
			all nine training blocks in the training folds.
		}
		\label{fig:iterations}
	\end{figure}

@@

	\begin{figure}
		%\includegraphics[width=\linewidth]{figures/accuracy.eps}
		\caption{Accuracy of the different classifiers for all 21 subjects relative to the
			number of blocks available for training. One block consists of 135
			epochs and corresponds to 27 seconds of stimulation. Accuracies
			are shown for the evaluation settings averaging over 1, 2, and
			3 trials of testing stimuli.
			\autoref{ap:accuracy_ap} contains results for all numbers of trials.
			While \textsc{stbf-emp} is unstable when little training data
			are available,
			regularization of the covariance matrix (\textsc{stbf-shrunk} and
			\textsc{stbf-struct}) drastically improves performance.}
		\label{fig:accuracy}
	\end{figure}
	\begin{table}[h]
		\centering
		\input{part2/stbf_struct_tests_1.tex}
		\caption{$p$-values calculated by one-sided paired Wilcoxon rank-sum test with
			Holm correction using one testing trial for different classifiers
			and levels of data availability. $p$-values $<0.05$ are considered significant
			and marked in grey.}
		\label{tab:p_values_1}

		\centering
		\input{part2/stbf_struct_tests_2.tex}
		\caption{$p$-values as in \autoref{tab:p_values_1} averaging over two testing trials.}
		\label{tab:p_values_2}

		\centering
		\input{part2/stbf_struct_tests_3.tex}
		\caption{$p$-values as in \autoref{tab:p_values_1} averaging over five testing trials.}
		\label{tab:p_values_5}
	\end{table}
	\unskip

@@

	\begin{figure}
		%\includegraphics[width=\linewidth]{figures/training_time.eps}
		\caption{Median fold training time for different classifiers at different spatial
			resolution levels evaluated over all training folds for all subjects.
			Error bars represent standard deviation. The training time of \textsc{stbf-shrunk} increases more
			steeply with resolution compared to \textsc{stbf-struct}.
			All \textsc{stbf} classifiers can be trained significantly faster than
			x\textsc{dawn+rg}.}
		\label{fig:training_time}
	\end{figure}

@@

>>>>

	\begin{figure}
		\includegraphics[width=\linewidth]{figures/stbf_struct/covs.eps}
		\caption{Different estimators of the covariance and inverse covariance
			of 100 epochs of data from \textit{Subject 01} for channels
			\textit{Fz}, \textit{Cz}, \textit{Pz}, and \textit{Oz} and time samples between 0.1s and 0.6s.
			Regularized estimators of the inverse covariance exhibit less extreme values and have a sparser structure.
			(\textbf{a,b}) Empirical covariance and inverse covariance matrices.
			(\textbf{c,d}) Shrunk covariance and inverse covariance matrices with $\alpha=0.14$ as
			determined by the closed-form LOOCV method. (\textbf{e,f}) Kronecker-Toeplitz
			structured covariance and inverse covariance matrices.
			(\textbf{g,h}) Spatial Kronecker factor of the Kronecker-Toeplitz structured shrunk estimator and its inverse.
			(\textbf{i,j}) Temporal Kronecker factor of the Kronecker-Toeplitz structured shrunk estimator and its inverse.}
		\label{fig:kronlda-covs}
	\end{figure}
	\todo{visualize kronecker sum}
	\todo{visualize kronpca decomp pvl}
	\todo{method pvl}

@@

  \begin{figure}
		\includegraphics[width=\linewidth]{figures/stbf_struct/fpi.eps}
		\caption{Average cross-validated \textsc{stbf-struct} Accuracy using
			one trial per block over all 21 subjects
			relative to the number of iterations used to estimate the Kronecker-Toeplitz structured shrunk
			covariance. Error bars represent the first and third quartiles. The
			accuracy does not improve when using more than one iteration.
			(\textbf{a}) Results for 1, 2, and 5 trials using only the first block in each
			training fold for training. (\textbf{b}) Results
			for 1, 2, and 5 trials using
			all nine training blocks in the training folds.
		}
		\label{fig:iterations}
	\end{figure}

@@

  \begin{figure}
		\includegraphics[width=\linewidth]{figures/stbf_struct/accuracy.eps}
		\caption{Accuracy of the different classifiers for all 21 subjects relative to the
			number of blocks available for training. One block consists of 135
			epochs and corresponds to 27 seconds of stimulation. Accuracies
			are shown for the evaluation settings averaging over 1, 2, and
			3 trials of testing stimuli.
			\autoref{ap:accuracy_ap} contains results for all numbers of trials.
			While \textsc{stbf-emp} is unstable when little training data
			are available,
			regularization of the covariance matrix (\textsc{stbf-shrunk} and
			\textsc{stbf-struct}) drastically improves performance.}
		\label{fig:accuracy}
	\end{figure}
	\begin{table}[h]
		\centering
		\input{chapters/stbf_struct_tests_1.tex}
		\caption{$p$-values calculated by one-sided paired Wilcoxon rank-sum test with
			Holm correction using one testing trial for different classifiers
			and levels of data availability. $p$-values $<0.05$ are considered significant
			and marked in grey.}
		\label{tab:p_values_1}

		\centering
		\input{chapters/stbf_struct_tests_2.tex}
		\caption{$p$-values as in \autoref{tab:p_values_1} averaging over two testing trials.}
		\label{tab:p_values_2}

		\centering
		\input{chapters/stbf_struct_tests_3.tex}
		\caption{$p$-values as in \autoref{tab:p_values_1} averaging over five testing trials.}
		\label{tab:p_values_5}
	\end{table}
	\unskip

@@

	\begin{figure}
		\includegraphics[width=\linewidth]{figures/stbf_struct/training_time.eps}
		\caption{Median fold training time for different classifiers at different spatial
			resolution levels evaluated over all training folds for all subjects.
			Error bars represent standard deviation. The training time of \textsc{stbf-shrunk} increases more
			steeply with resolution compared to \textsc{stbf-struct}.
			All \textsc{stbf} classifiers can be trained significantly faster than
			x\textsc{dawn+rg}.}
		\label{fig:training_time}
	\end{figure}

@@

  \todo{Include part kronlda, check notes in journal}
\section{Introduction}

LCMV struct might be to restrictive
Toeplitzlda
MEG paper

\section{Methods}
\subsection{Spatiotemporal Linear Discriminant Analysis}
\subsection{The single Kronecker product covariance model}
\begin{equation}
	\mat{C} = \mat{S}\otimes\mat{T}
\end{equation}
Tapering, Toeplitz and shrinkage
\subsection{The Kronecker sum covariance model}
\begin{equation}
	\mat{C} = \sum_k^{CS}\mat{S}\otimes\mat{T}
\end{equation}
pvl, kronpca

\subsection{Kronecker sum covariance estimation}
\subsection{Classification}
\section{Results}
\section{Discussion}

\todo{check chapters/structure paper}
\todo{check structure Leuven.ai poster}
\section{The spatiotemporal EEG covariance}
\section{The single-KP covariance model}
\section{The sum-of-KP covariance model}
\section{Decoding performance}
\section{Extension into the space-time-frequency domain}
